Baseline centering problem

### 2019-01-12 paper/tangotd.tex

>>>>

It's a bit strange to train the policy for goal $s_2$ via policy gradient,
instead of just selecting the next state to maximize
$z(s,s_2;s_2)$ where $z(s,s_2;s_3)$ is the $z$ function associated with
the policy that has goal $s_3$. Formally, computing the latter is
feasible: one has to follow an exploration policy that has a non-constant
goal,so at each step we observe a transition of the policy with some goal
$s_3$; and hope that Newton--Bellman for computing $z(s,s_2;s_3)$
generalizes well with respect to $z_3$.
